---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

```{r}
median_vector <- c()
for(i in 1:1000)
{
  new_sample <- sample(airquality$Solar.R, replace = TRUE)
  new_sample <- na.omit(new_sample)
  median_vector <- c(median_vector, median(new_sample))
}
quantile_mean <- quantile(median_vector, c(0.25, 0.75))
print(paste("Confidence Interval left-side: ", quantile_mean[1]))
print(paste("Confidence Interval right-side: ", quantile_mean[2]))
```

```{r}
library(boot)


med <- function(data, i)
{
  new_sample <- na.omit(data[i])
  return(median(new_sample))
}

se = boot(airquality$Solar.R, med, 1000)
mean_solar <- se$t0
se
```
So the confidence interval is from 205 - 12.3 = 206.7, 205 + 12.3 = 217.3
The first method is easier to use.

```{r}
library('COUNT')
```


```{r}
ships$Risk = ships$incidents > 10
ships$Risk[ships$Risk == TRUE] = "High"
ships$Risk[ships$Risk == FALSE] = "Low"
```


```{r}
table(ships$Risk)
```
Yes because the condition of CLT(at least 30 samples) is not satisfied we need simulation.

```{r}
library('mosaicData')
plot(Galton$father, Galton$height, xlab = "Father Height", ylab = "Kid height", main = "Father hight and his child height 
     diagram")
```

Yes it seems like most of the points are close to a line.

```{r}
corr_height <- cor(Galton$father, Galton$height)
print(paste("Correlation height is: ", corr_height))
```
No because the correlation coeffiecent is a low number thus we couldn't conclude strong relationship between variables.

```{r}
lm_height <- lm(Galton$height ~ Galton$father, data = Galton)
lm_height
```

This variables define a line which is the best approximation for the relation between response and explanatory variable.

```{r}
plot(Galton$father, Galton$height, xlab = "Father Height", ylab = "Kid height", main = "Father hight and his child height 
     diagram")
abline(39.1104, 0.3994, col = "red", lwd = 3)
```
It means when the father height is 0 what would be the kid height(It doesnt show anything most of the time).
```{r}
predict(lm(height ~ father, data = Galton), newdata = data.frame(father = c(70, 75, 80)))
```

```{r}
lm_height_mother <- lm(height ~ father + mother, data = Galton)
lm_height_mother
```
```{r}
resid_height <- resid(lm_height_mother)
hist(resid_height)
```
It should be similar to normal distribution

```{r}
qqnorm(resid_height)
qqline(resid_height)
```
By checking the Linearity of the residuals compare to normal we could check whether it is similar to normal distribution or not.

```{r}
plot(resid_height ~ Galton$father)
abline(0, 0)
plot(resid_height ~ Galton$mother)
abline(0, 0)
```
It checks the Constant Variability conditions for MLR. That is should be randomly distributed around 0.

```{r}
plot(resid_height)
```

It checks Independent Residuals in MLR conditions.

```{r}
lm_three <- lm(Galton$height ~ Galton$father + Galton$mother + Galton$sex)
summary(lm_three)
```

Yes it is statistically significant because its p-value as we can see above is less than 0.01

```{r}
library('MASS')
nf <- subset(Galton, select = -c(family))
lm_selection <- lm(height ~ ., data = nf)
backward_lm <- stepAIC(lm_selection, direction = "backward")
summary(backward_lm)
```
```{r}
resid_back <- resid(backward_lm)
hist(resid_back)
qqnorm(resid_back)
qqline(resid_back)
plot(resid_back)
```
```{r}
library('COUNT')
data('titanic')
titanic$new_survived[titanic$survived == "yes"] = TRUE
titanic$new_survived[titanic$survived == "no"] = FALSE
titanic$new_survived <- factor(titanic$new_survived)
titanic <- subset(titanic, select = -c(survived))
titanic_glm <- glm(titanic$new_survived ~ ., data = titanic, family = "binomial")
summary(titanic_glm)
```
```{r}
person_sample <- data.frame(class = "2nd class", age = "adults", sex = "man")
predict(titanic_glm, newdata = person_sample, type = "response")
```
```{r}
all_possible <- titanic %>% expand(class = c('1st class', '2nd class', '3rd class'), age, sex)
all_possible$prob_survive <- predict(titanic_glm, newdata = all_possible, type = "response")
sorted_possible <- all_possible[order(-1 * all_possible$prob_survive), ]
sorted_possible
```
```{r}
pred <- predict(titanic_glm, newdata = titanic, type = "response")
titanic$survive_pred <- pred
titanic$survive_pred2[titanic$survive_pred > 0.5] = TRUE
titanic$survive_pred2[titanic$survive_pred < 0.5] = FALSE
print(paste("precentage correct is: ", sum(titanic$survive_pred2 == titanic$new_survived) / nrow(titanic)))
```
No is is not going to be valid because there are alot of different variable in two ships. 
