---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---
Statistical Inference Lab1 

Aryan Soltani



1.
```{r}
norm_x <- seq(-3, 3, length = 1000)
norm_y <- dnorm(norm_x)
plot(norm_x, norm_y, type = "l", xlab = "x", ylab = "norm(x)", main = "Normal distribution within range [-3, 3]")
```

2. 
```{r}
x <- rnorm(5)
hist(x)
x <- rnorm(10)
hist(x)
x <- rnorm(100)
hist(x)
x <- rnorm(1000)
hist(x)
```
The one with 1000 number of samples has produced the most accurate answer, and the more sample we have the more accurate histogram we would get.
```{r}
t_x <- seq(-3, 3, length = 1000)
colors <- c("red", "green", "blue", "purple")
df_plots <- c(1, 2, 5, 10)
plot(t_x, dt(t_x, df_plots[1]), col = colors[1], main = "
     T-student Plots", ylab = "Y-Axis", xlab = "X-Axis", lwd = 0.5) 
for(i in 2:4)
{
  lines(t_x, dt(t_x, df_plots[i]), col = colors[i]) 
}
legend("topleft", c("df = 1", "df = 2", "df = 5", "df = 10"), col = colors, lty = c(1,1,1,1))
```


```{r}
hist(precip)
hist(rnorm(80, mean = mean(precip), sd = sd(precip)))
```

They are similar and the precipitation distribution is very close to normal distribution.


```{r}
norm_y <- rnorm(1000)
hist(norm_y, breaks = 7)
hist(norm_y, breaks = 13)
hist(norm_y, breaks = 30)
hist(norm_y, breaks = 13, density = 10)
```
The one with the density visualized the data better than the others and between the histograms with different bins the one with the more bins has visualized better.
```{r}
hist(norm_y, breaks = 13, prob = TRUE, col = "grey", main = "Histogram and its density curve", xlab = "X-axis", 
     ylab = "Y-axis")
lines(density(norm_y, adjust = 3), col = "red", lwd = 2)
legend("topright", c("Histogram", "Density of the histogram"), col = c("grey", "red")
       , lty = c(1, 1, 1, 1))
```

```{r}
whiskers = boxplot(rivers)
```
As we can see in the boxplot the rivers dataset is right-skewed.    

```{r}
whiskers
```
The whiskers values is 135 and 1205 and theses can be extract as the stats output of return value of the boxplot
and yes there are some outliers above the upper whisker and their exact values are [ 1459 1450 1243 2348 3710 2315 2533 1306 1270 1885 1770]

```{r}
group_1 = rivers[rivers < 500]
group_2 = rivers[rivers < 1500]
group_3 = rivers[rivers < 3000]
group_4 = rivers[rivers >= 3000]
vec_count_group = c(length(group_1), length(group_2), length(group_3), length(group_4))
vec_count_group = (vec_count_group * 100) / sum(vec_count_group)
pie(vec_count_group, col = c("red", "blue", "green", "purple"),  label = paste0(
  round(vec_count_group) , "%  " , c("tiny", "short", "medium", "long")))
  
```

```{r}
data()
mtcars
boxplot(mtcars$disp ~ mtcars$hp)
```
It is showing the box for each category within their disp value and the ~ symbol is used for showing the formula.
```{r}
library(ggplot2)


ggplot(Orange, aes(x = age, y = circumference)) + geom_point()
```
```{r}
ggplot(Orange, aes(x = age, y = circumference)) + geom_point(aes(size = Tree), color = "red")
```


```{r}
ggplot(Orange, aes(x = age, y = circumference)) + geom_smooth()
```
It is using the loess method.
```{r}
Orange$AgeGroup = Orange$age

colour <- c("blue", "royalblue4", "green", "springgreen4", "pink")

Orange$AgeGroup[Orange$age <= 250] = "Young"
Orange$AgeGroup[Orange$age > 250 & Orange$age <= 900] = "Adult"
Orange$AgeGroup[Orange$age > 900] = "Old"

ggplot(Orange, aes(fill = Tree, x = AgeGroup, y = circumference)) + geom_bar(stat = "identity", position="dodge") + coord_flip() + ggtitle("Growth of Orange Trees") + scale_fill_manual("legend", values = colour)
``````

